Dual-Mode PSK Transceiver on SDR With FPGA

### 2024-01-06 latex/paper.tex
Add Behav Simulation in Paper
Verilog + Python + LaTeX for the interesting TikZ drawing!

\usetikzlibrary{svg.path,shapes.symbols,shapes.misc}
\definecolor{orcidlogocol}{HTML}{A6CE39}
\tikzset{
  orcidlogo/.pic={
    \fill[orcidlogocol] svg{M256,128c0,70.7-57.3,128-128,128C57.3,256,0,198.7,0,128C0,57.3,57.3,0,128,0C198.7,0,256,57.3,256,128z};
    \fill[white] svg{M86.3,186.2H70.9V79.1h15.4v48.4V186.2z}
                 svg{M108.9,79.1h41.6c39.6,0,57,28.3,57,53.6c0,27.5-21.5,53.6-56.8,53.6h-41.8V79.1z M124.3,172.4h24.5c34.9,0,42.9-26.5,42.9-39.7c0-21.5-13.7-39.7-43.7-39.7h-23.7V172.4z}
                 svg{M88.7,56.8c0,5.5-4.5,10.1-10.1,10.1c-5.6,0-10.1-4.6-10.1-10.1c0-5.6,4.5-10.1,10.1-10.1C84.2,46.7,88.7,51.3,88.7,56.8z};
  }
}

@@

% \makesavenoteenv{tabular}
\interdisplaylinepenalty=2500
\aboverulesep = 0mm \belowrulesep = 0mm
\newcolumntype{Y}{>{\centering\arraybackslash}X}
\newcolumntype{M}[1]{>{\centering\arraybackslash}m{#1}} % centered m
\newcommand{\tabvertspace}{\specialrule{0em}{0.08em}{.08em}}

@@

@@

>>>>

\usetikzlibrary{svg.path,shapes.symbols,shapes.misc}
\usepgfplotslibrary{fillbetween}
\definecolor{orcidlogocol}{HTML}{A6CE39}
\tikzset{
  orcidlogo/.pic={
    \fill[orcidlogocol] svg{M256,128c0,70.7-57.3,128-128,128C57.3,256,0,198.7,0,128C0,57.3,57.3,0,128,0C198.7,0,256,57.3,256,128z};
    \fill[white] svg{M86.3,186.2H70.9V79.1h15.4v48.4V186.2z}
                 svg{M108.9,79.1h41.6c39.6,0,57,28.3,57,53.6c0,27.5-21.5,53.6-56.8,53.6h-41.8V79.1z M124.3,172.4h24.5c34.9,0,42.9-26.5,42.9-39.7c0-21.5-13.7-39.7-43.7-39.7h-23.7V172.4z}
                 svg{M88.7,56.8c0,5.5-4.5,10.1-10.1,10.1c-5.6,0-10.1-4.6-10.1-10.1c0-5.6,4.5-10.1,10.1-10.1C84.2,46.7,88.7,51.3,88.7,56.8z};
  }
}

@@

% \makesavenoteenv{tabular}
\interdisplaylinepenalty=2500
\aboverulesep = 0mm \belowrulesep = 0mm
\newcolumntype{Y}{>{\centering\arraybackslash}X}
\newcolumntype{M}[1]{>{\centering\arraybackslash}m{#1}} % centered m
\newcommand{\tabvertspace}{\specialrule{0em}{0.08em}{.08em}}
\renewcommand\tabularxcolumn[1]{m{#1}}% for vertical centering text in X column

@@

      The transmitter DAC simulaiton results are shown in Fig.~\ref{fig:tx_dac_sim}.
      \begin{figure}[h]
        \setlength{\tabcolsep}{2pt}
        \subfloat[BPSK modulation.]{%
          \sffamily\notsotiny
          \begin{tabularx}{\linewidth}{@{}lX@{}}
            clk\_1M024 & \input{tikz/sim/Tx_BPSK_clk_1M} \\
            clk\_16M384 & \input{tikz/sim/Tx_BPSK_clk_16M} \\
            DAC\_bits[1:0] & \input{tikz/sim/Tx_BPSK_bits} \\
            DAC\_bits[1] & \input{tikz/sim/Tx_BPSK_bits_1} \\
            \textcolor{gray}{DAC\_bits[0]} & \input{tikz/sim/Tx_BPSK_bits_0} \\
            DAC\_I[11:0] & \input{tikz/sim/Tx_BPSK_DAC_I} \\
            DAC\_Q[11:0] & \input{tikz/sim/Tx_BPSK_DAC_Q} \\
          \end{tabularx}%
        }\hfill%
        \subfloat[QPSK modulation.]{%
          \sffamily\notsotiny
          \begin{tabularx}{\linewidth}{@{}lX@{}}
            clk\_1M024 & \input{tikz/sim/Tx_QPSK_clk_1M} \\
            clk\_16M384 & \input{tikz/sim/Tx_QPSK_clk_16M} \\
            DAC\_bits[1:0] & \input{tikz/sim/Tx_QPSK_bits} \\
            DAC\_bits[1] & \input{tikz/sim/Tx_QPSK_bits_1} \\
            DAC\_bits[0] & \input{tikz/sim/Tx_QPSK_bits_0} \\
            DAC\_I[11:0] & \input{tikz/sim/Tx_QPSK_DAC_I} \\
            DAC\_Q[11:0] & \input{tikz/sim/Tx_QPSK_DAC_Q} \\
          \end{tabularx}%
        }
        \caption{DAC simulation results of the transmitter.}
        \label{fig:tx_dac_sim}
      \end{figure}

@@

  \section{Figures in This Paper}
